---
title: "broom: tidy model information"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{broom}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

+--------------+------------------------------------------------------+
| Col1         | Col2                                                 |
+==============+======================================================+
| -   `tidy`   | -   summarizes information about model components    |
+--------------+------------------------------------------------------+
| -   `glance` | -   reports information about the entire model       |
+--------------+------------------------------------------------------+
| -            | -   adds information about observations to a dataset |
|    `augment` |                                                      |
+--------------+------------------------------------------------------+

# Introduction

[Broom](https://broom.tidymodels.org/index.html) helps creating tidier
statistical methods

```{r}
library(tidymodels)
```

```{r}
ggplot(mtcars, aes(mpg, wt)) + 
    geom_point()
```

Let's say we want to fit a nonlinear model to the weight/mileage
relationship in the `mtcars` data set. We can use the `nls` function to
determine the nonlinear (weighted) least-squares estimates of the
nonlinear model.

    nlsfit <- nls(formula=mpg ~ k / wt + b, data= mtcars, start = list(k = 1, b = 0))
    summary(nlsfit)

As we can see this is a non-tidy output.

We can generate 2000 bootstrap samples replicates of the data using
`bootstraps` for sampling with replacement.

```{r}
set.seed(27)
boots <- bootstraps(mtcars, times = 2000, apparent = TRUE)
```

```{r}
fit_nls_on_bootstrap <- function(split) {
    nls(mpg ~ k / wt + b, analysis(split), start = list(k = 1, b = 0))
}
```

Now, we can map this function to the bootstraps and map tidy, glance and
augment to get a tidy coefficients information.

```{r}
regressions <-  boots %>% 
  mutate(model = map(splits, fit_nls_on_bootstrap),
         tidied = map(model, tidy),
         glanced = map(model, glance),
         augmented = map(model, augment)
         )
```

If we inspect `regressions` we can see that tidied, glanced and
augmented column contain ***nested lists*** with 5, 4 and 9 variables
each respectively.

```{r}
regressions
```

We can select 200 random bootstrap and unnest `augment()` to visualize
the uncertainty in the fitted curve.

```{r}
regressions %>% 
    sample_n(200) %>%
    unnest(augmented) %>% 
    ggplot( aes(wt, mpg)) +
    geom_line(aes(y = .fitted, group = id), alpha = .2, col = "blue") +
    geom_point()
```

# Additional links

-   You can contribute to implementing additional tidying methods. Check
    out [available tidy
    methods](https://broom.tidymodels.org/articles/available-methods.html)
    and the principles to implement them
    [here](https://www.tidymodels.org/learn/develop/broom/#implement-tidying-methods)

-   For more additional explanations of how to interpret output of
    linear regression model check
    [dsbox](https://rstudio-education.github.io/datascience-box/course-materials/slides/u4-d02-fitting-interpreting-models/u4-d02-fitting-interpreting-models.html#7).
