---
title: "infer: statistical inference"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{infer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(mariatidymodels)
library(dplyr)
library(infer)
```

### Exploring infer

The most useful verbs in infer to ply with statistical inference are:

-   `specify()` specifies the variable, or relationship between variables, of interest
-   `hypothesize()` declare the null hypothesis. It can be independence of two variables or a mean number.
-   `generate()` generates resamples
-   `calculate()` calculates summary estatistics taking as input from hypothesize() or generate()

Let's generate some random datapoints with beta distribution

```{r generating-data, warning = FALSE, message = FALSE}
set.seed(123)
transcript <- tibble(
    name   = sample(letters,25),
    cor   = rbeta(25,1,3))
```

Let's calculate the mean of this distribution

```{r}
cor_mean <- transcript %>%
    specify(response = cor) %>%
    calculate(stat = "mean")
```

The problem at task is to determine which of those correlations is statistically significant.

```{r}
null_distn <- transcript %>%
    specify(response = cor) %>%
    hypothesize(null = "point", mu = as.numeric(cor_mean)) %>%
    generate(reps = 1000, type = "bootstrap") %>%
    calculate(stat = "mean")
```

We can get the confidence interval for a given ⍺ level.

```{r}
percentile_ci <- get_confidence_interval(null_distn, level = 0.95)

```

We can visualise those results with a nice ggplot object

```{r}
visualize(null_distn,bins = 20) +
    shade_confidence_interval(endpoints = percentile_ci)
```

My little wrapper for this particular task

```{r simulate}
simulator(numer=25, bins=20)
```

# Source 

This article is inspired by the t_test article on [infer pkgdown.](https://infer.netlify.app/articles/t_test.html) I added `get_confidence_interval` and `shade_confidence_interval` functions to add information about CI as well as generate my own `simulator` function to automate this process.
